Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-29 paper/paper.tex
Add labels

@@

\todo[inline]{Grafica de dispersion dificultad para identificar cada tipo de etiqueta}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=0.6\textwidth]{labels.png}
  \caption{Graphical representation of the relative difficulty of each type of annotation. We compute the relative number of systems that correctly identified each annotation of each type. Boxplots show the mininum, maximum, and interquartile range.\label{fig:labels}}
\end{figure*}

Figure~\ref{fig:labels} compares annotation labels according to their relative difficulty. We define the difficulty of a specific annotation~(e.g., a specific entity or relation instance in the testing set) as the relative number of systems that correctly identified that annotation.
Afterwards, we compute the interquartile range of the difficulty score for each of the annotations in the testing set.
The figure suggests that entities are, on average, easier to recognize than relations, which is consistent with the superior results obtained in Subtask A compared to Subtask B by all participants.

@@
